---
title: "Example got-to script"
description: ""
date: "`r format(Sys.Date(), format='%B %d %Y') `"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example-script}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Example Script Using R Package `GAPsurvey`

> Last updated April 2024

Open Rstudio script `example_script.R`. This should already be located on desktop, otherwise find it using the link below. 

```{r find-example-script}
system.file("r/example_script.R", package = "GAPsurvey")
```
## Install R package

Rerun this only when there is a new version of the package to install. The user may install from `GitHub`:

```{r install-github, eval = FALSE}
devtools::install_github("afsc-gap-products/GAPsurvey")
```

or install from local file `.tar.gz`:

```{r install-local, eval = FALSE}
# example, the user may have a different path
install.packages('C:/Users/User/Downloads/GAPsurvey_2023.04.04.tar.gz',
                 repos=NULL, type='source')
```

## Load libraries

```{r load-packages}
library(GAPsurvey)
```

Now we can use functions from `GAPSurvey`! 

## What have we historically caught at this station?

Learn more about and find examples using...

```{r get_catch_haul_history, eval =  FALSE}
?get_catch_haul_history
```

```{r get_catch_haul_history-use}
get_catch_haul_history(
  years = 2021:2023, # optional; if you only want to see a specific year, not the last 10
  species_codes = c(21720, 21740), # optional; pacific cod and walleye pollock ONLY
  survey = "EBS", # for example
  station = "I-13") # for example
```

## What time is sunrise and sunset?

Learn more about and find examples using...

```{r get_sunrise_sunset, eval =  FALSE}
?get_sunrise_sunset
```

```{r get_sunrise_sunset-use}
get_sunrise_sunset(chosen_date = "2024-06-10",
                   survey = "AI",
                   station = "33-47")

get_sunrise_sunset(chosen_date = Sys.Date(),
                   survey = "GOA",
                   station = "323-176")

get_sunrise_sunset(chosen_date = "2024-08-04",
                   survey = "EBS",
                   station = "P-31")

get_sunrise_sunset(chosen_date = "2024-06-04",
                   survey = "NBS",
                   station = "ZZ-01")

get_sunrise_sunset(chosen_date = "2024-08-04",
                   survey = NULL,
                   latitude = 60,
                   longitude = -162)
```

## Convert CTD data to BTD as a backup for SBE39 (aka 'the BT')

```{r convert_ctd_btd, eval =  FALSE}
?convert_ctd_btd
```

```{r convert_ctd_btd-use, eval = FALSE}
convert_ctd_btd(
  filepath_hex = system.file(paste0("exdata/convert_ctd_btd/",
                                    "SBE19plus_01908106_2023_06_18_0001.hex"),
                             package = "GAPsurvey"),
  filepath_xmlcon = system.file(paste0("exdata/convert_ctd_btd/",
                                       "SBE19plusV2_8106_ph_DO_leg2.xmlcon"),
                                package = "GAPsurvey"),
  VESSEL = 162,
  CRUISE = 202301,
  HAUL = 97,
  latitude = 59.01693, # Approximate - for depth estimation
  MODEL_NUMBER = "",
  VERSION_NUMBER = "",
  SERIAL_NUMBER = 8106)
```


