---
title: "Example got-to script"
description: ""
date: "`r format(Sys.Date(), format='%B %d %Y') `"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example-script}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Example Script Using R Package "GAPsurvey"

> Last updated April 2024

Open Rstudio script "example_script.R" (should be located on desktop, if you have this opened in R, you are already here! This is the example_script.R file!)

## Load Packages (only need to do this once

# install R package

Rerun this only when there is a new version of the package to install
```{r install-github, eval = FALSE}
devtools::install_github("afsc-gap-products/GAPsurvey")
```

or

```{r install-local, eval = FALSE}
install.packages('C:/Users/User/Downloads/GAPsurvey_2023.04.01.tar.gz',
                 repos=NULL, type='source')
```

## Load libraries

```{r load-packages}
library(GAPsurvey)
```

## Use functions from `GAPSurvey`

### What have we historically caught at this station?

## Learn more about and find examples using...

```{r get_catch_haul_history, eval =  FALSE}
?get_catch_haul_history
```

```{r get_catch_haul_history-use}
get_catch_haul_history(
  # years = 2021, # optional; if you only want to see a specific year, not the last 10
  # species_codes = c(21720, 21740), # optional; pacific cod and walleye pollock ONLY
  survey = "EBS", # for example
  station = "I-13") # for example
```

### What time is sunrise and sunset?

## Learn more about and find examples using...

```{r get_sunrise_sunset, eval =  FALSE}
?get_sunrise_sunset
```

```{r get_sunrise_sunset-use}
get_sunrise_sunset(chosen_date = Sys.Date(),
                  survey = "EBS",
                  station = "I-13")

get_sunrise_sunset(chosen_date = "2023-06-10",
                   survey = "GOA",
                   station = "7-7")

get_sunrise_sunset(chosen_date = "2023-06-10",
                   latitude = 52.6,
                   longitude = -169.4364)
```

